---
title: "Regression models project"
---


1. Preprocessing

First we will take the mtcars dataset from dplyr library
```{r}
library(dplyr)
library(MASS)
library(ggplot2)
library("car")
library("lmtest")
```

Explore dataset
```{r}
data("mtcars")
summary(mtcars)
```

2. Analysis

We will check for the relations between mpg and other variables by checking the correlation
```{r}
cor(mtcars$mpg, mtcars[,-1])
```
3. Is an automatic or manual transmission better for MPG ?

We assume in the mtcars dataset that 
  . 1 = automatic
  . 0 = manual
  
We will convert the value of am variable into "Automatic" and "Manual" words 
```{r}
mtcars$am <- as.factor(mtcars$am)
levels(mtcars$am) <-c("Automatic", "Manual")
```

We will have box plot the mpg by automatic and manual car

```{r}
boxplot(mtcars$mpg ~ mtcars$am, data = mtcars, ylab = "miles per gallon", xlab = "transmission type", col = "red")
```
As we see in the box plot, the automatic has less mpg in general than the manual car. We will also do the t-test between the 2 mean mpg of these types of transmission to check for our hypothesis

```{r}
t.test(mtcars$mpg ~ mtcars$am)
```
As we see the p-value = 0.001374 << 0.05. So we can reject the null hypothesis that the difference in mean is equal to 0. We accept that mpg by automatic is less than mpg by manual car.

3. Quantify the MPG difference between automatic and manual transmissions

In order to tell the difference, we need to use multiple linear regression analysis
```{r}
model <- lm(mpg ~ ., data = mtcars)
summary(model)
```
We want to find the best model, so we will use stepAIC
```{r}
model <- stepAIC(model, direction = 'both')
summary(model)
```

We can finally reduced the number of variables into 3 variables: wt, qsec and am. However we can't clearly see the impact of wt and qsec on automatic and manual car.
We will try to optimize our model

```{r}
model <- lm(mpg ~ factor(am):wt + factor(am):qsec, data = mtcars)
summary(model)
```
We can see the R-squared has increased from 84.97% to 89.46%. 
  _ When weight increases by 1000 lbs, the mpg of automatic cars decreased by -3.1759 and the mpg of manual cars decreased by -6.0992
  _ For the qsec, when 1/4 mile time increased, the mpg increased 0.8338 for automatic cars and 1.4464 for manual cars.
  
For verification of our model, we will check the LINE assumption of multiple linear regression:

```{r}
plot(model,1)
```
```{r}
qqnorm(model$residuals, pch = 1, frame = FALSE)
qqPlot(model$residuals)
```
```{r}
dwtest(model)
```
p-value >> 0.05 we accept the null hypothesis that residuals are independent
From the plots of residuals vs fitted values, plot of normality and test for independence. We can say that our model is significant. 

4. Conclusion
The mpg is determined mainly by weight, acceleration and transmission type. We cannot decide which car has better mpg just based only on the transmission type but also on the weight and acceleration of the car. 

